
\documentclass{article} % For LaTeX2e
\usepackage{iclr2026_conference,times}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage[hidelinks]{hyperref}
\usepackage{url}


\title{Exhaustive Markov Blanket Discovery}

% Authors must not appear in the submitted version. They should be hidden
% as long as the \iclrfinalcopy macro remains commented out below.
% Non-anonymous submissions will be rejected without review.

\author{Loong Kuan Lee \& Ragavi Krishnamoorthy\\
Hybrid Intelligence\\
Fraunhofer IAIS\\
Sankt Augustin, Germany\\
\texttt{\{loong.kuan.lee,ragavi.krishnamoorthy\}@iais.fraunhofer.de}\\
\And
Allegra Cuzzocera\\
Department of Physics Ettore Pancini \\
University of Naples Federico II \\
Naples, Italy \\
\texttt{allegra.cuzzocrea@unina.it} \\
\And
Nico Piatkowski \\
Hybrid Intelligence\\
Fraunhofer IAIS\\
Sankt Augustin, Germany\\
\texttt{nico.piatkowski@iais.fraunhofer.de}\\
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}


\maketitle

%%% Abstract
\begin{abstract}
  The problem of learning the Markov blanket (MB) of a variable from
  data has applications in many areas such as learning Bayesian
  networks, causal discovery, and feature selection. However, for a
  dataset with $n+1$ variables, enumerating every possible MB for a
  target variable $t$ has a complexity that's exponential to
  $n$. Previous approaches have employed advanced techniques to avoid
  fully exploring this exponential search space. However, these methods
  are not exhaustive, and therefore incapable of consistently capturing
  certain higher order relationships between variables; most notably,
  xor relationships between $t$ and $2$ other binary
  variables. Therefore, we will revisit the problem of exhaustive MB
  discovery by using techniques from the field of frequent itemset
  mining to help prune the exponential search space. Specifically, we
  propose a method called Lattice Incremental Association Mining for
  Markov Blanket discovery (LIAM-MB) which just adds an additional phase
  between the two phases of Incremental Association Markov Blanket
  (IAMB)---one of the first approches to MB discovery. Experiments on
  synthetic Bayesian networks containing xor and parity relationships
  shows that LIAM-MB is able to capture those relationships while other
  approaches are unable to. Further experiments on common benchmark
  datasets will show the cost LIAM-MB incurs for being an exhaustive
  search compared to existing MB discovery approaches, in particular
  against its parent method IAMB.
\end{abstract}

%%% Intro
\section{Introduction}
%%%% What is MB Discovery
The Markov blanket (MB) discovery problem is...
dataset $\db$, target variable $t$

originally discussed in the context of learning Bayesian
networks~\citep{margaritis1999,tsamardinos2003}

However has been later discussed and used in feature selection and
causal discovery.
%%%% Why is MB Discovery hard
A naive approach to MB discovery would just involve enumerating over all
the possible MBs of the target variable $t$. However the number of
possible MBs is exponential with respect to $n$,
\begin{equation}
  \label{eq:1}
  \sum_{i=1}^{n}\binom{n}{i}=2^{n},
\end{equation}
where $n$ is the number of variables in $\db$ other than $t$. Therefore
this 

An exhaustive enumeration of all possible 

%%% Related Work
\section{Related Work}




%%% Method
\section{Method}


%%% Post matter
\subsubsection*{Author Contributions}
If you'd like to, you may include  a section for author contributions as is done
in many journals. This is optional and at the discretion of the authors.

\subsubsection*{Acknowledgments}
Use unnumbered third level headings for the acknowledgments. All
acknowledgments, including those to funding agencies, go at the end of the paper.



\bibliography{ref}
\bibliographystyle{iclr2026_conference}

\appendix
\section{Appendix}
You may include other additional sections here.


\end{document}
